---
title: "Generational Differences in Attitudes on How to Get Ahead"
author: "Mike Silva"
date: "11 September 2014"
output:
  pdf_document: default
  html_document:
    theme: cerulean
---

```{r echo=FALSE, cache=TRUE , message=FALSE}
load(url("http://bit.ly/dasi_gss_data"))
library(dplyr)
library(plyr)
library(ggplot2)

gss$birth.year <- gss$year - gss$age

get.generation <- function(birth.year){
  if(birth.year %in% 1883:1900){return('1-Lost')}
  else if(birth.year %in% 1901:1927){return('2-Greatest')}
  else if(birth.year %in% 1928:1945){return('3-Silent')}
  else if(birth.year %in% 1946:1964){return('4-Baby Boomer')}
  else if(birth.year %in% 1965:1980){return('5-Gen X')}
  else if(birth.year %in% 1981:2015){return('6-Millennial')}
  else{return('7-Unknown')}
}

gss$generation <- as.factor(sapply(gss$birth.year, get.generation))

## Relabel the generations
gss$generation <- revalue(gss$generation, c('1-Lost'='Lost', '2-Greatest'='Greatest', '3-Silent'='Silent', '4-Baby Boomer'='Baby Boomer', '5-Gen X'='Gen X', '6-Millennial'='Millennial','7-Unknown'='Unknown'))
```

### Introduction:

Insert introduction here...

### Data:

This analysis uses data from the General Social Survey (GSS).  The GSS is conducted face-to-face with an in-person interview by the National Opinion Research Center at the University of Chicago.  The universe is adults (18+) in randomly selected households. responses range from `r min(gss$year)` to `r max(gss$year)`.

```{r, echo=FALSE}
ggplot(gss, aes(x = generation, fill=generation)) + geom_bar() + ggtitle('Figure 1: Number of Respondents by Generation') + theme(axis.title.x = element_blank()) + ylab('Count') + theme(legend.position='none')
```


### Exploratory data analysis:

Insert exploratory data analysis here...
```{r}
table(gss$getahead, gss$generation)
```


### Inference:

Insert inference section here...

### Conclusion:

Insert conclusion here...
